\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}

### 2022-12-14 R/Supp_Info_1.Rmd
Building a skeleton for the supplementary material

---
title: "\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}"
output: 
  html_document
---

@@

@@

![Degree of collaboration _versus_ technical difficulty (sequential)](../content/images/scatterblob_1-viridis-turbo.png)

>>>>

---
output:
  bookdown::pdf_document2:
      latex_engine: xelatex
      number_sections: false
      toc: false
mainfont: "Times New Roman"
geometry: margin = 1in
spacing: double
fontsize: 11pt
editor_options:
  markdown:
    wrap: sentence
csl: https://raw.githubusercontent.com/marlonecobos/kuenm/master/ecography.csl
link-citations: yes
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}\doublespacing
   - \usepackage{parskip}
   - \setlength{\parindent}{4em}
   - \setlength{\parskip}{0em}
   - \usepackage{caption}
   - \usepackage{pdflscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}
---

@@

## Study

### Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution

### Supplementary Information 1

### Representing technical difficulty and degree of collaboration in use cases for Github in ecology and evolution

**Appendix S1.1. Computing indices of technical difficulty and degree of collaboration**

We aimed at distributing the use cases discussed in our study across gradients of technical difficulty and collaboration.
For this, we [...].

We then [\...].

We used Google Docs and Google Sheets to manipulate data, and plotted results using `R` version 4.02.

\noindent

**Appendix S1.2. Annotated code and prose allowing the representation of indices of technical difficulty and degree of collaboration**

@@

![Degree of collaboration *versus* technical difficulty (sequential)](../content/images/scatterblob_1-viridis-turbo.png)
